---
title:           Five Km Analysis
author:          Dennis Wollersheim
date:            14.07.2020
linkcolor:       cyan
citecolor:       grey
output:
  pdf_document:
    highlight:   zenburn
---

\tableofcontents

```{r load_data}

source('_drake.R')

loadd(df_hospitals)
#loadd(df_neighbours)
loadd(df_pt_segments_small)

loadd(df_final)




```

mesh blocks intersection with 5km circle, to determine population density




# Base Hospital Dataset Descriptive stats

```{r descriptive_stats_initial}

df_hospitals %>%
  count( state, beds ) %>% pivot_wider(id_cols=state, names_from = beds, values_from=n) %>%
  janitor::clean_names() %>%
  select( state, x50, x50_99, x100_199, x200_500, x500, null ) %>%
  gt() %>%
  tab_header(
             title = "Hospital Dataset",
             subtitle = "Number of institutions by size and and state  "
  ) %>%
  cols_label(
             x50 = "<50",
             x50_99 = "50-99",
             x100_199 = "100-199",
             x200_500 = "200-500",
             x500 = ">500",
             null = 'Unknown'
  )

```

# PT accessible Hospital Descriptive stats

```{r descriptive_stats_}

df_hospitals %>%
  left_join( df_pt_segments_small %>% distinct(id) %>%   mutate(has_pt='has_pt'  ) ) %>%
  count( state, beds, has_pt ) %>%
  replace_na(list(n=0, has_pt='no_pt')) %>%
  pivot_wider(id_cols=c(state, beds), names_from = has_pt, values_from=n) %>%
  replace_na(list(no_pt=0, has_pt=0)) %>%
  mutate(pt_pct = has_pt / (has_pt+no_pt)) %>%
  select(-ends_with('pt')) %>%
  pivot_wider(id_cols=state, names_from = beds, values_from=pt_pct) %>%
  janitor::clean_names() %>%
  select( state, x50, x50_99, x100_199, x200_500, x500, null ) %>%
  gt() %>%
  tab_header(
             title = "Pt Accessible Hospitals",
             subtitle = "Percentage accessible by public transport"
             ) %>%
  fmt_percent(
              columns = 2:7,
              decimals = 1,
              drop_trailing_zeros = TRUE
  ) %>%
  data_color(
             columns = 2:7,
             colors = scales::col_numeric(
                                          palette = paletteer::paletteer_d(
                                                                           palette = "ggsci::red_material"
                                                                           ) %>% as.character(),
                                          domain = NULL
                                          ),
             alpha = 0.8
  ) %>%
  cols_label(
  x50 = "<50",
  x50_99 = "50-99",
  x100_199 = "100-199",
  x200_500 = "200-500",
  x500 = ">500",
  null = 'Unknown'
  ) %>%
  tab_footnote(
               footnote = "NA means there were no hospitals in this category",
               locations = cells_body( columns = vars(x500), rows = is.na(x500))
  )

```

# Hospitals that were unable to geocode to SA2 level

```{r descriptive_stats_2}


df_segments_sa %>%
  anti_join( df_segments_sa_remote, by='id' )  %>%
  distinct(id) %>%
  inner_join( df_hospitals)  %>%
  select(id, hospital_name, state, long, lat, beds, suburb, description) %>%
  gt()
```




# Dependent data variables
- number of segments
- total time

# Plan - Plots
time vs distance - box plot
box plot of total time by type
box plot of total time by type

coorelation plot of total time, description, beds, state, nsegments_walking, nsegments_transit, duration_walking, duration_transit, distance

range of distances

# plots

Note NSW and SA distance distributions have strange shapes,probably due to the algorithm that translates random points into directions, and the location of the ocean with respect to their hospitals

```{r plots1}

df_pt_segments_small %>%
  inner_join( df_hospitals , by='id') %>%
  ggplot( aes( state, dist)) + geom_boxplot()

df_pt_segments_small %>%
  inner_join( df_hospitals , by='id') %>%
  group_by( state) %>%
  summarise( n(), sd(dist), mean(dist)) %>%
  gt()


```

Note, many of the hospitals could not get 10 directions out of the 20 that we tried.  The random point allocation process is a blunt instrument

```{r}


df_pt_segments_small %>%
  inner_join( df_hospitals , by='id') %>%
  count(id, state) %>%
  ggplot( aes( n )) + geom_histogram() +
  facet_wrap(~state)

```
Note, this strange distribution does not apply to the bed variable

```{r}


df_pt_segments_small %>%
  inner_join( df_hospitals , by='id') %>%
  ggplot( aes( beds, dist)) + geom_boxplot()

df_pt_segments_small %>%
  inner_join( df_hospitals , by='id') %>%
  group_by( beds ) %>%
  summarise( n(), sd(dist), mean(dist))


```


# Data engineering - accessibility by state
todo...


plot points for addresses, categorise them as to where they are;  remoteness

differece between settings

plot hospital

bed count, travel difference

state difference, rural vs urban

geocode the poeple,

remoteness clasification for each


seifa score for each person

sa1 index for seifa?


abs shape file for remoteness;  is something within



#Summary

```{r summary}

summary(df_final)
plot(df_final)

#plot variables only
df_final %>%
  select( dist, duration_transit, duration_walking, distance_transit, distance_walking, n_segments_transit, n_segments_walking,  IRSD_score, RA_CODE16, state, bed_cat, beds, description ) %>%
  plot()

df_final %>%
  select( id, dist, arrival_time, departure_time, duration_transit, duration_walking, distance_transit, distance_walking, n_segments_transit, n_segments_walking,  SA1_7DIG16, IRSD_score, RA_CODE16, hospital_name, state, postcode, bed_cat, beds, description ) %>%
  mutate( total_time = arrival_time - GLOBAL_BASE_DATE_TIME ) %>%
  mutate( total_pt_duration = duration_transit + duration_walking) %>%
  mutate( total_pt_distance = distance_transit + distance_walking) %>%
  mutate_if( is_character, as_factor)  %>%
  { . } -> df_final_subset

summary(df_final_subset)

```


```{r plot1}

ggplot(df_final_subset, aes(x = IRSD_score, y = total_pt_duration, color = dist)) +
  geom_jitter(size = 3)

ggplot(df_final_subset, aes(x = total_pt_duration, y = dist, color = beds)) +
  geom_jitter(size = 3)

ggplot(df_final_subset, aes(x = total_pt_distance, y = dist, color = beds)) +
  geom_jitter(size = 3)


df_final_subset %>%
  filter( id==1070)


df_final_subset %>%
  group_by(id) %>%
  summarise_if(is.numeric, list( mean=mean, sd=sd)) %>%
  inner_join( df_hospitals, by='id') %>%
  write_csv( 'data/means.csv')


readd(df_hospitals_sa_remote) %>%
  select( id,RA_CODE16, IRSD_score ) %>%
  inner_join( df_final_subset, by='id', suffix=c('.hospital', '.remote') ) %>%
  write_csv('data/remotes_with_hosptial_coding.csv')





```







